Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2019-10-08 manuscript/manuscript.tex
changes

\gc{The presence of an unselected control line provides an alternative way to
  partition the effects of linked selection and genetic drift: we can compare
  the total variance in allele frequency change of the control line (which
  excludes the effect of artificial selection on allele frequencies) to the
  total variance in frequency change of the Longshanks selection
  lines.
We can partition the allele frequency change between the two timepoints (20
  generations) for a Longshanks line as $\Delta p_{t,\mathrm{LS1}} =
  \Delta_{_{D1}} p_{t,\mathrm{LS1}} + \Delta_{_{U1}} p_{t} +
  \Delta_{_\mathrm{LS}} p_t$ 
  where these  terms in are the decomposition are the allele frequency change due to
  drift in replicate 1 ($D1$),
  selection unique to the 1$^{st}$ LS replicate ($U1$), and selection response shared between the
  two Longshanks replicates (LS) respectively (and similarly for the Longshanks two line, LS2).
  %partition the allele frequency change between the two timepoints (20
  %generations) for a Longshanks line as $\Delta p_{t,\mathrm{LS1}} =
  % \Delta_{_D} p_{t,\mathrm{LS1}} + \Delta_{_{U}} p_{t,\mathrm{LS1}} +
  % \Delta_{_\mathrm{LS}} p_t$ (and similarly for the Longshanks two line, LS2),
  % and $\Delta p_{t,\mathrm{Ctrl}} = \Delta_{_D} p_{t,\mathrm{Ctrl}} +
  % \Delta_{_{U}} p_{t,\mathrm{Ctrl}} + \Delta_{_\mathrm{Ctrl}} p_t$ for the
  % control line. Here, $\Delta_{_D} p_{t}$, $\Delta_{_U} p_t$,
  % $\Delta_{_\mathrm{LS}} p_t$ are the allele frequency changes due to drift,
  % selection unique to a replicate, and selection response shared between the
  % two Longshanks replicates, respectively.
  By construction we will assume that each of these terms
  are uncorrelated within replicates, and that only the shared term
  covaries between the replicates. Assuming that we can approximate the
  contribution of genetic drift in the LS
  lines the variance in allele frequency change observed in
  the control ($\var(\Delta p_{t,\mathrm{Ctrl}})
  = \var(\Delta_{_D1} p_{t})=\var(\Delta_{_D2} p_{t})$), then we can estimate the increase in variance in allele
  frequency change due to selection as $(\var(\Delta p_{t,\mathrm{LS1}}) +
  \var(\Delta p_{t,\mathrm{LS2}}))/2 - \var(\Delta p_{t,\mathrm{Ctrl}})$ and
  the shared effect of selection across selected lines as $\cov(\Delta
  p_{t,\mathrm{LS1}}, \Delta p_{t,\mathrm{LS2}})$. We estimate at least 32\%
    (95\% CI $[21\%, 48\%]$) of the variance in allele frequency change is
    driven by the effects of selection, of which 14\% (95\% CI $[3\%, 33\%]$)
    is estimated to be unique to a selection line, and 17\% (95\% CI $[9\%,
  23\%]$) is the effect of shared selection between the two Longshanks
selection lines.}

>>>>

\gc{The presence of an unselected control line provides an alternative way to
  partition the effects of linked selection and genetic drift: we can compare
  the total variance in allele frequency change of the control line (which
  excludes the effect of artificial selection on allele frequencies) to the
  total variance in frequency change of the Longshanks selection
  lines.
We can partition the allele frequency change between the two timepoints (20
  generations) for a Longshanks line as $\Delta p_{t,\mathrm{LS1}} =
  \Delta_{_{D1}} p_{t,\mathrm{LS1}} + \Delta_{_{U1}} p_{t} +
  \Delta_{_\mathrm{LS}} p_t$ 
  where these  terms in are the decomposition are the allele frequency change due to
  drift in replicate 1 ($D1$),
  selection unique to the 1$^{st}$ LS replicate ($U1$), and selection response shared between the
  two Longshanks replicates (LS) respectively (and similarly for the Longshanks two line, LS2).
  %partition the allele frequency change between the two timepoints (20
  %generations) for a Longshanks line as $\Delta p_{t,\mathrm{LS1}} =
  % \Delta_{_D} p_{t,\mathrm{LS1}} + \Delta_{_{U}} p_{t,\mathrm{LS1}} +
  % \Delta_{_\mathrm{LS}} p_t$ (and similarly for the Longshanks two line, LS2),
  % and $\Delta p_{t,\mathrm{Ctrl}} = \Delta_{_D} p_{t,\mathrm{Ctrl}} +
  % \Delta_{_{U}} p_{t,\mathrm{Ctrl}} + \Delta_{_\mathrm{Ctrl}} p_t$ for the
  % control line. Here, $\Delta_{_D} p_{t}$, $\Delta_{_U} p_t$,
  % $\Delta_{_\mathrm{LS}} p_t$ are the allele frequency changes due to drift,
  % selection unique to a replicate, and selection response shared between the
  % two Longshanks replicates, respectively.
  By construction we will assume that each of these terms
  are uncorrelated within replicates, and that only the shared term
  covaries between the replicates. Assuming that we can approximate the
  contribution of genetic drift in the LS
  lines the variance in allele frequency change observed in
  the control, i.e. $\var(\Delta p_{t,\mathrm{Ctrl}})
  = \var(\Delta_{_D1} p_{t})=\var(\Delta_{_D2} p_{t})$, then we can estimate the increase in variance in allele
  frequency change due to selection as $(\var(\Delta p_{t,\mathrm{LS1}}) +
  \var(\Delta p_{t,\mathrm{LS2}}))/2 - \var(\Delta p_{t,\mathrm{Ctrl}})$ and
  the shared effect of selection across selected lines as $\cov(\Delta
  p_{t,\mathrm{LS1}}, \Delta p_{t,\mathrm{LS2}})$. We estimate at least 32\%
    (95\% CI $[21\%, 48\%]$) of the variance in allele frequency change is
    driven by the effects of selection, of which 14\% (95\% CI $[3\%, 33\%]$)
    is estimated to be unique to a selection line, and 17\% (95\% CI $[9\%,
  23\%]$) is the effect of shared selection between the two Longshanks
selection lines.}
